Report with embedded R code

### 2022-04-04 Project/FinalReport.Rmd
add table1

@@

```{r}
PCltrsMod1 <- lm(PC1 ~ site*treat, data = ltrs_pc)
summary(PCltrsMod1)
anova(PCltrsMod1)
```

```{r}
PCltrsMod2 <- lm(PC2 ~ site*treat, data = ltrs_pc)
summary(PCltrsMod2)
anova(PCltrsMod2)
```

```{r}
PCltrsMod3 <- lm(PC3 ~ site*treat, data = ltrs_pc)
summary(PCltrsMod3)
anova(PCltrsMod3)
```

## Ploting PCA

>>>>

The following chunks are used to make table 1 attached in the poster.

@@

```{r}
PCltrsMod1 <- lm(PC1 ~ site*treat, data = ltrs_pc)
summary(PCltrsMod1)
anova(PCltrsMod1)
```
p-value <0.05 suggests there is no significant evidence in favor of a potential relationship between component 1 and factors including treatment type and elevation sites except median-elevation. Specifically, the linear regression line is steepest for the plants normally transplanted(TR) to median elevation.

```{r}
PCltrsMod2 <- lm(PC2 ~ site*treat, data = ltrs_pc)
summary(PCltrsMod2)
anova(PCltrsMod2)
```
p-value <0.05 suggests there is significant evidence in favor of a potential relationship between component 2 and factors including elevation and treatment.

```{r}
PCltrsMod3 <- lm(PC3 ~ site*treat, data = ltrs_pc)
summary(PCltrsMod3)
anova(PCltrsMod3)
```
p-value >0.05 suggests there is no significant evidence in favor of a potential relationship between component 3 and factors including elevation and treatment.

### Table 1
![pca analysis table 1](https://github.com/zazauwu/432_Group5/blob/main/Project/Figure/pca%20table.png)
## Ploting PCA
